%% PROPOSAL: Generation of elliptic curves for circuit use.
%% Marta, Barry and Jordi.
%% The 2nd ZKProof Workshop 2019.

\documentclass{article}

% Packages
	\usepackage[colorlinks=true,
				urlcolor=black,
				linkcolor=black,
				citecolor=black
				]{hyperref} 
	
	\usepackage[english]{babel}
	\usepackage[utf8]{inputenc}
	\usepackage{amsmath, amsthm, amssymb, mathtools}
	\usepackage{enumerate, enumitem}
	\usepackage{graphicx, color, xcolor}
	\usepackage{setspace}
	\usepackage{authblk}
	\usepackage{braket}
	
	\usepackage{algorithm}
	\usepackage[noend]{algpseudocode}
	\makeatletter
	\def\BState{\State\hskip-\ALG@thistlm}
	\makeatother
	
	\usepackage{listings}
	\lstdefinelanguage{Sage}[]{Python}
	{morekeywords={False,sage,True},sensitive=true}
	\lstset{frame=none,
			showtabs=False,
			showspaces=False,
			showstringspaces=False,
			commentstyle={\ttfamily\color{dgreencolor}},
			keywordstyle={\ttfamily\color{dbluecolor}\bfseries},
			stringstyle={\ttfamily\color{dgraycolor}\bfseries},
			language=Sage,
			basicstyle={\fontsize{10pt}{10pt}\ttfamily},
			aboveskip=0.3em,
			belowskip=0.1em,
			numbers=none,%left,
			numberstyle=\footnotesize
			}
		
	\definecolor{dblackcolor}{rgb}{0.0,0.0,0.0}
	\definecolor{dbluecolor}{rgb}{0.01,0.02,0.7}
	\definecolor{dgreencolor}{rgb}{0.2,0.4,0.0}
	\definecolor{dgraycolor}{rgb}{0.30,0.3,0.30}
	\newcommand{\dblue}{\color{dbluecolor}\bf}
	\newcommand{\dred}{\color{dredcolor}\bf}
	\newcommand{\dblack}{\color{dblackcolor}\bf}

% Commands	
	\newcommand{\N}{\ensuremath{\mathbb{N}}}
	\newcommand{\Np}{\ensuremath{\mathbb{N}^{+}}}
	\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
	\newcommand{\Q}{\ensuremath{\mathbb{Q}}}
	\newcommand{\R}{\ensuremath{\mathbb{R}}}
	\newcommand{\C}{\ensuremath{\mathbb{C}}}
	\newcommand{\Fp}{\ensuremath{\mathbb{F}_p}}
	\newcommand{\Fr}{\ensuremath{\mathbb{F}_r}}
	\newcommand{\G}{\ensuremath{\mathbb{G}}}
	\newcommand{\point}[1]{P_{#1} = (x_{#1}, y_{#1})}
	\newcommand{\llog}{\log_2}
	\newcommand{\xor}{\oplus}
	\newcommand{\minSize}{1.5em}
	\newcommand{\gen}[1]{\ensuremath{\langle #1\rangle}}
	\newcommand{\noi}{\noindent}
	\newcommand{\red}[1]{\textcolor{red}{#1}}
	\newcommand{\blue}[1]{\textcolor{blue}{#1}}

% Margins
	\textwidth 16 cm
	\textheight 23.5 cm
	\topmargin -1.5 cm
	\oddsidemargin -0 cm
	
	\addtolength{\skip\footins}{1pc plus 5pt} % Foot note space
	\setlength\parindent{0pt} % No indent

% Title
	\makeatletter
	\renewcommand\AB@affilsepx{, \protect\Affilfont}
	\makeatother

	\title{Generation of (Twisted Edwards) elliptic curves for circuit use 
			\vspace{-0.2cm} }
	\author[1]{Barry WhiteHat}
	\author[2]{Jordi Baylina}
	\author[2,3]{Marta Bellés}
	\affil[1]{Ethereum foundation}
	\affil[2]{iden3}
	\affil[3]{Universitat Pompeu Fabra}
	\setcounter{Maxaffil}{0}
	\renewcommand\Affilfont{\itshape\small}

\begin{document}
\begin{spacing}{1.2}	

\maketitle  	  \vspace{1.5cm}
\tableofcontents  \vspace{0.5cm}


\newpage

%%
\section{Scope, motivation and background}
	
	Motivation:
	\begin{itemize}
		\item 	Protocols like zk-SNARK require the usage of pairing-friendly elliptic curves (references to SNARK, pairing-friendly elliptic curves and BN, BL).
		\item 	What happens if inside the circuit we need to implement protocols that use elliptic curves, such as Pedersen Hash and EdDSA. 
		\item 	Inside the SNARK, we have elements of a certain field $\Fp$ (which is the order of the pairing-friendly curve, is at always of prime order?)
		\item 	So, we have to find what we call an {\it embedded curve} defined over $\Fp$.
	\end{itemize}
	
	Aim:
	\begin{itemize}
		\item 	This proposal aims to define a deterministic algorithm for generating elliptic curves defined over a given prime field. 
				That is, given a prime $p$, generate an elliptic curve defined over $\Fp$.
		\item 	It is important the ability to find it in a deterministic way---so that it was clear no other considerations were taken for defining---is 
				paramount as it significantly reduces the possibility of a backdoor being present, thus leading to better security.
		\item 	Also: provide an algorithm for checking its safety against best known attacks. 
		\item 	We present an example of a generated curve done this way: Baby Jubjub. Also include the arithmetic implementation of it. 
	\end{itemize}

	Background:
	\begin{itemize}
		\item Elliptic curve? Pairing-friendly (BN, BL)? Twisted Edwards / Montgomery elliptic curve? (Add REF).
		\item Order of the elliptic curve? Large prime dividing the order?
		\item Safety criteria: add attacks? (Add REF?)
	\end{itemize}
	
	Terminology:
	\begin{itemize}
		\item {\it Embedded elliptic curve}: given an elliptic curve $E$ of prime order $p$, an elliptic curve $E'$ defined over $\Fp$ is called an embedded elliptic curve of $E$. 
	\end{itemize}

	Notation:
	\begin {table}[h!]
		\centering
		\begin{tabular}{|c|l|}
			\hline
			{\bf Notation} 	& {\bf Description} \\ 
			\hline
			{$E$} 			& Twisted Edwards elliptic curve.\\ 
			\hline		
			{$p$} 			& Prime number. Characteristic of the field $E$ is defined over.\\ 
			\hline
			\begin{tabular}{@{}c@{}}	{$a$}  \\ {$d$} \end{tabular}
				  			& Parameters of the equation $ax^2 + y^2 = 1 +  d x^2 y^2$.\\ \hline
			{$n$} 			& Order of the curve. Typically, $n = h\times l$. \\ 
			\hline
			{$l$} 			& Large prime dividing the order of the curve.\\ 
			\hline
			{$h$} 			& Cofactor.\\ 
			\hline
			{$x_0, y_0$} 	& Generator of the curve.\\ 
			\hline
			{$x_1, y_1$} 	& Generator of the large prime subgroup of the curve.\\ 
			\hline
		\end{tabular}
		\label{tab:notation}
	\end{table}

%%
\section{Generation of embedded elliptic curves}
	Definition of the curve:
	\begin{itemize}
		\item Finite field (defined by $p$).
		\item Order of the curve and its prime decomposition* (in case of TEd/Mont: cofactor and large prime).
		\item Generator and base point.
	\end{itemize}
	
	%%
	\subsection{Twisted Edwards and Montgomery}
	%TODO: Write and justify the assumptions.
				
		In 2016, a group of researchers of IRPF designed a deterministic algorithm that, given a prime number $p$, it returns the elliptic curve defined over $\Fp$ with smallest coefficient $A$ such that $A-2$ is a multiple of 4 and equation $y^2 = x^3 + Ax^2 + x$ describes a Montgomery curve. 
		The assumption $A-2$ divisible by 4 comes from the fact that as this value is used in many operations, so trying to keep it smaller and divisible by four is a reasonable assumption \cite{generation-baby}.
		
		\subsubsection{Generation of elliptic curves given $p$ with $p\equiv1\mod4$} \input{gen-curves}\vspace{0.5cm}
				
		\subsubsection{Generation of elliptic curves given $p$ with $p\equiv3\mod4$}
		%TODO: Add text
		
	%% 
	%TODO
	\subsection{Elliptic curves of prime order}
	\subsection{Pairing-friendly elliptic curves}

%%
\section{Safety criteria}
	% TODO
	SafeCurves is a project that checks some of the most common and known attacks on several elliptic curves. It also provides the algorithm it was used \cite{safe-curves}.
	
	\begin{itemize}
		\item 
	\end{itemize}

%%
\section{Example: embedded curve of BN128 generation of Baby Jubjub}
	
	%%
	\subsection{Generation Of Baby Jubjub}
		We considered the large prime number dividing the order of BN128 and run algorithm A.1 from \cite{generation-baby}. The first elliptic curve it was returned  satisfying SafeCurves criteria was the Montgomery curve with coefficient $A = 168698$. We named this curve Baby Jubjub elliptic curve. 

		\subsubsection{Code}
		\input{gen-curves-bjj}\vspace{0.5cm}

	%%
	\subsection{Definition Of Baby Jubjub}
		From now on, let 
			$$	p = 21888242871839275222246405745257275088548364
					400416034343698204186575808495617 $$
		and $\Fp$ the finite field with $p$ elements. 
		
		%%
		\subsubsection{Montgomery Form}
			We define $E_M$ as the {\it Baby-Jubjub} Montgomery elliptic curve defined over $\Fp$ given %described
			by equation
			$$	E: v^2 = u^3 +  168698u^2 + u. $$
			The order of $E_M$ is $n = 8\times l$, where 
			$$	l = 2736030358979909402780800718157159386076813972
			158567259200215660948447373041 $$ 
			is a prime number. Denote by $\G$ the subgroup of points of order $r$, that is, %of $E$ 
			$$\G = \Set{ P \in E(\Fp) | l P = O  }.$$

		%%
		\subsubsection{Edwards Form}
			$E_M$ is birationally equivalent to the Edwards elliptic curve %[REF] defined by  
				$$	E: x^2 + y^2 = 1 +  d x^2 y^2 $$
			where
			$ d = 9706598848417545097372247223557719406784115219466060233080913168975159366771.$ \\
			
			The birational equivalence \cite[Thm. 3.2]{twisted} from $E$ to $E_M$ is the map
			% These results are from \cite[Theorem 3.2]{twisted}. 
			$$ (x,y) \to (u,v) = \left( \frac{1 + y}{1 - y} , \frac{1 + y}{(1 - y)x} \right) $$
			with inverse from $E_M$ to $E$
			$$ (u, v) \to (x, y) = \left(  \frac{u}{v}, \frac{u - 1}{u + 1}   \right). $$

		%%
		\subsubsection{Parameters}
			\begin {table}[h!]
				\centering
				\begin{tabular}{|c|l|}
					\hline
					{\bf Notation} & {\bf Value}\\
					\hline
					{$p$} 	&	21888242871839275222246405745257275088548364400416034343698204186575808495617 \\
					\hline
					{$a$} 	& -1 \\
					\hline
					{$d$} 	& 12181644023421730124874158521699555681764249180949974110617291017600649128846 \\
					\hline
					{$n$} 	& 21888242871839275222246405745257275088614511777268538073601725287587578984328 \\
					\hline
					{$l$} 	& 2736030358979909402780800718157159386076813972158567259200215660948447373041 \\
					\hline
					{$h$} 	& 8 \\
					\hline
					{$x_0$} & 995203441582195749578291179787384436505546430278305826713579947235728471134 \\
					\hline
					{$y_0$} & 5472060717959818805561601436314318772137091100104008585924551046643952123905 \\
					\hline
					{$x_1$} & 5299619240641551281634865583518297030282874472190772894086521144482721001553 \\
					\hline
					{$y_1$} & 16950150798460657717958625567821834550301663161624707787222815936182638968203 \\
					\hline
				\end{tabular}
				\label{tab:baby-jubjub}
			\end{table}
	
	\subsection{Arithmetic In Baby Jubjub}
		In this section we define how to operate in the elliptic curve group: %two operations supported in the elliptic curve group: 
		the addition of points and multiplication of a point by a scalar (an element of $\Fp$).
		 	\subsubsection{Addition Of Points} \input{addition}
		 	\subsubsection{Multiplication Of A Point Of $E$ By A Scalar} \input{multiplication}

\section{Challenges And Security}
	As required in the construction of Baby-Jubjub, the curve satisfies SafeCurves criteria. This can be checked following \cite{github-barry}.
	
\section{Implementation}	
	Barry WhiteHat:	
	\begin{itemize}
		\item %Description, generation and cryptographic requirements:
		\url{https://github.com/barryWhiteHat/baby_jubjub}
		\item %Arithmetic:
		\url{https://github.com/barryWhiteHat/baby_jubjub_ecc} 
	\end{itemize}
	Jordi Baylina: \url{https://github.com/iden3/circomlib/blob/master/src/babyjub.js}

%%	
\section {Intellectual Property}

	We will release the final version of this proposal under creative commons, to ensure it is freely available to everyone.


%% References
\addcontentsline{toc}{section}{References}
	\bibliographystyle{acm}
	\bibliography{lit}
\end{spacing}	
\end{document}
